Implementing XBF: An Efficient Self-Describing Binary Format

### 2023-08-08 docs/paper.tex
Update paper

\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{listings}

@@

\begin{IEEEitemize}
	\item CSV (Comma Separated Values) \cite{csv_spec}\cite{csv_parser}
	\item MessagePack \cite{msgpack_spec}\cite{msgpack_parser}
	\item CBOR (Concise Binary Object Representation) \cite{cbor_spec}\cite{cbor_parser}
	\item JSON \cite{json_parser}
	\item XML \cite{xml_parser}
\end{IEEEitemize}

>>>>

\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xurl}
\usepackage{xcolor}
\usepackage{listings}

@@

\begin{IEEEitemize}
	\item CSV (Comma Separated Values)\cite{csv_spec}\cite{csv_parser}
	\item MessagePack\cite{msgpack_spec}\cite{msgpack_parser}
	\item CBOR (Concise Binary Object Representation)\cite{cbor_spec}\cite{cbor_parser}
	\item JSON\cite{json_parser}
	\item XML\cite{xml_parser}
\end{IEEEitemize}
